\documentclass{article}
\usepackage{amssymb}
\usepackage{enumerate}
\usepackage{enumitem}


\title{Pre-Workshop Survey}
\author{For the 2018-2019 Data Science Workshops at Montana State University}
\date{}

\newlist{todolist}{itemize}{2}
\setlist[todolist]{label=$\square$}

\begin{document}

\maketitle

\vspace{0.25cm}

\noindent You are being asked to participate in a research study to understand what methods are the most
effective in teaching computational skills in \texttt{R}. Results from this study may provide a better
understanding of the computational thinking and abilities of undergraduate and graduate students. \\

\noindent If you agree to participate in this study you will be asked to complete a pre-workshop survey, detailing
your demographic information and computational background and a post-workshop assessment of your
understanding of the computational techniques covered. Your survey and assessment will be paired and
any information that might identify you personally (including your name) will be removed. Only the
workshop administrator will have access to your identity. \\

\noindent Your participation in this research is voluntary. You are free to stop participating in the research at any
time, or to decline to answer any specific questions. Your participation in this research study is
confidential. There are no foreseen risks to participation in this research study. \\

\noindent If you have any questions regarding this research project you can contact me at allisontheobold@montana.edu. \\

\begin{enumerate}
    \item I agree to participate in the study. 
    If you agree to participate, you will be asked to complete all of the questions below.
    \begin{todolist}
        \item Yes
        \item No
    \end{todolist}

%     \item Please enter a unique identifier as follows: Number of pets (as numeric) + First two letters
% of your last name (lowercase) + First three letters of your current street (lowercase). 

    \item Please indicate your relevant departmental affiliation. Check all that apply.
    \begin{todolist}
        \item Agricultural Economics 
        \item Agricultural Education
        \item Animal \& Range Sciences
        \item Land Resources \& Environmental Sciences
        \item Microbiology \& Immunology
        \item Plant Sciences \& Plant Pathology
        
        \item Architecture
        \item Art
        \item Film \& Photography
        \item Music
        
        \item Education
        \item Health \& Human Development
        
        \item Center for Biofilm Engineering
        \item Chemical \& Biological Engineering
        \item Civil Engineering
        \item Computer Science
        \item Electrical \& Computer Engineering
        \item Mechanical \& Industrial Engineering
        \item Nursing
        
        \item Agricultural Economics 
        \item Chemistry \& Biochemistry
        \item Earth Sciences
        \item Ecology
        \item Organismal Biology (Botany, Zoology, etc.)
        \item Planetary Sciences (Geology, Climatology, Oceanography, etc.)
        \item English
        \item History \& Philosophy
        \item Mathematical Sciences
        \item Native American Studies
        \item Physics
        \item Political Science
        \item Psychology
        \item Sociology and Anthropology
        
        \item Economics or Business
        \item Space Sciences
        \item Other (please specify)
    \end{todolist}
    
    \item Your current occupation at the university 
    \begin{todolist}
        \item Seeking Bachelors degree
        \item Seeking Master's degree 
        \item Seeking Doctorate degree
        \item Completing a Post-Doc
        \item Faculty member
        \item Staff Member 
        \item Other (please specify)
        \end{todolist}

    \item How many computer science courses (undergrad or grad) have you taken?  
    
    \item What are your previous computer science experiences? List course names.  
    
    \item What programming languages do you have experience with? Check all that apply.
    \begin{todolist}
        \item Python
        \item \texttt{R}
        \item Java or Javascript
        \item C or C++
        \item Fortran
        \item MatLab or Mathematica
        \item SQL 
        \item Other (please specify)
        \item None
        \item What is a programming language?
        \end{todolist}
        
    \item What are your previous statistics experiences? List course names.   
    
    \item What other courses have you taken that require computer programming (e.g. R, GIS, SPSS, STATA, SAS, MatLab, Mathematica, MARK, etc.)? List course names. 
    
    \item What operating system is on the computer you are bringing to the workshop?
    \begin{todolist}
        \item OSX
        \item Windows
        \item Linux or Ubuntu
        \item What is an operating system?
        \end{todolist}
        
    \item Have you participated in independent or collaborative research outside the classroom? 
    \begin{todolist}
        \item Yes
        \item No
        \end{todolist}

\newpage        

    \item If so, how much? Check all that apply.
    \begin{todolist}
        \item Little to No
        \item A few projects
        \item I'm almost done with my thesis
        \item I completed a thesis
        \end{todolist}
        
    \item Do you have experience collecting your own data? Check all that apply.
    \begin{todolist}
        \item Yes, I've helped others collect data.
        \item Yes, I've collected my own data, 
        \item No
        \end{todolist}
    
    \item If you have collected your own data, how did you choose to store it? Check all that apply.
    \begin{todolist}
        \item Microsoft Excel
        \item Microsoft Access
        \item Microsoft Word
        \item On paper
        \item Text file
        \item Other (please specify) 
        \end{todolist}
        
    \item What is your most important reason for attending this workshop? Check all that apply.
    \begin{todolist}
        \item Research assistance
        \item Coursework assistance
        \item Preparation for graduate school
        \item Adviser recommended
        \item Department/Professor recommended
        \item Network with other workshop attendees
        \item Refresh or update skills
        \item Other (please specify)
        \end{todolist}
        
    \item What resources have you used while learning to program in \texttt{R}? Check all that apply.
    \begin{todolist}
        \item Peers
        \item Lab Mates
        \item Adviser
        \item Course Materials
        \item Internet Resources
        \item Other (please specify)
        \end{todolist}

\newpage 

    \item In a few words, what do you hope to learn from this workshop?
    
\end{enumerate}

\end{document}