---
title: "Code for Analysis of Survey Data"
author: "Allison Theobold, Stacey Hancock, & Sara Mannheimer"
date: "December 15, 2019"
output: pdf_document
---
# Set-up Options  

```{r}
library(tidyverse)
library(forcats)
library(lubridate)
```

# Read in Data  

```{r data}
introR <- read_csv("introR_survey_raw.csv")
intermedR <- read_csv("intermediateR_survey_raw.csv")
wrangle <- read_csv("wrangle_survey_raw.csv")
viz <- read_csv("viz_survey_raw.csv")
```


# Cleaning Column Names

```{r}

introR <- introR %>% 
  rename(survey_time = Timestamp, 
         identifier = `Please enter a unique identifier as follows: Number of pets (as numeric) + First two letters of your last name (lowercase) + First three letters of your current street (lowercase).  (e.g. I have no pets, my last name is Theobold, and I live on Beall Street, my unique identifier would be 0thbea)`,
         department = `Please indicate your relevant departmental affiliation. Check all that apply.`,
         occupation = `Your current occupation at the university`, 
         cs_course_count = `How many computer science courses (undergrad or grad) have you taken?`, 
         cs_course_name = `What are your previous computer science experiences? List course names.`, 
         cs_languages = `What programming languages do you have experience with? Check all that apply.`, 
         stat_course_name = `What are your previous statistics experiences? List course names.`, 
         other_programming_course = `What other courses have you taken that require computer programming (e.g. R, GIS, SPSS, STATA, SAS, MatLab, Mathematica, MARK, etc.)? List course names.`, 
         operating_system = `What operating system is on the computer you are bringing to the workshop?`, 
         research_experience = `Have you participated in independent or collaborative research outside the classroom?`, 
         research_amount = `If so, how much? Check all that apply.`, 
         data_collect_experience = `Do you have experience collecting your own data? Check all that apply.`, 
         data_storage = `If you have collected your own data, how did you choose to store it? Check all that apply.`, 
         reason_attend = `What is your most important reason for attending this workshop? Check all that apply.`, 
         resources_used = `What resources have you used while learning to program in R? Check all that apply.`, 
         hope_learn = `In a few words, what do you hope to learn from this workshop?`
         ) 


intermedR <- intermedR %>% 
  rename(survey_time = Timestamp, 
         identifier = `Please enter a unique identifier as follows: Number of pets (as numeric) + First two letters of your last name (lowercase) + First three letters of your current street (lowercase).  (e.g. I have no pets, my last name is Theobold, and I live on Beall Street, my unique identifier would be 0thbea)`,
         department = `Please indicate your relevant departmental affiliation. Check all that apply.`,
         occupation = `Your current occupation at the university`, 
         cs_course_count = `How many computer science courses (undergrad or grad) have you taken?`, 
         cs_course_name = `What are your previous computer science experiences? List course names.`, 
         cs_languages = `What programming languages do you have experience with? Check all that apply.`, 
         stat_course_name = `What are your previous statistics experiences? List course names.`, 
         other_programming_course = `What other courses have you taken that require computer programming (e.g. R, GIS, SPSS, STATA, SAS, MatLab, Mathematica, MARK, etc.)? List course names.`, 
         operating_system = `What operating system is on the computer you are bringing to the workshop?`, 
         research_experience = `Have you participated in independent or collaborative research outside the classroom?`, 
         research_amount = `If so, how much? Check all that apply.`, 
         data_collect_experience = `Do you have experience collecting your own data? Check all that apply.`, 
         data_storage = `If you have collected your own data, how did you choose to store it? Check all that apply.`, 
         reason_attend = `What is your most important reason for attending this workshop? Check all that apply.`, 
         resources_used = `What resources have you used while learning to program in R? Check all that apply.`, 
         hope_learn = `In a few words, what do you hope to learn from this workshop?`
         )


wrangle <- wrangle %>% 
  rename(survey_time = Timestamp, 
         identifier = `Please enter a unique identifier as follows: Number of pets (as numeric) + First two letters of your last name (lowercase) + First three letters of your current street (lowercase).  (e.g. I have no pets, my last name is Theobold, and I live on Beall Street, my unique identifier would be 0thbea)`,
         department = `Please indicate your relevant departmental affiliation. Check all that apply.`,
         occupation = `Your current occupation at the university`, 
         cs_course_count = `How many computer science courses (undergrad or grad) have you taken?`, 
         cs_course_name = `What are your previous computer science experiences? List course names.`, 
         cs_languages = `What programming languages do you have experience with? Check all that apply.`, 
         stat_course_name = `What are your previous statistics experiences? List course names.`, 
         other_programming_course = `What other courses have you taken that require computer programming (e.g. R, GIS, SPSS, STATA, SAS, MatLab, Mathematica, MARK, etc.)? List course names.`, 
         operating_system = `What operating system is on the computer you are bringing to the workshop?`, 
         research_experience = `Have you participated in independent or collaborative research outside the classroom?`, 
         research_amount = `If so, how much? Check all that apply.`, 
         data_collect_experience = `Do you have experience collecting your own data? Check all that apply.`, 
         data_storage = `If you have collected your own data, how did you choose to store it? Check all that apply.`, 
         reason_attend = `What is your most important reason for attending this workshop? Check all that apply.`, 
         resources_used = `What resources have you used while learning to program in R? Check all that apply.`, 
         hope_learn = `In a few words, what do you hope to learn from this workshop?`
         )


viz <- viz %>% 
  rename(survey_time = Timestamp, 
         identifier = `Please enter a unique identifier as follows: Number of pets (as numeric) + First two letters of your last name (lowercase) + First three letters of your current street (lowercase).  (e.g. I have no pets, my last name is Theobold, and I live on Beall Street, my unique identifier would be 0thbea)`,
         department = `Please indicate your relevant departmental affiliation. Check all that apply.`,
         occupation = `Your current occupation at the university`, 
         cs_course_count = `How many computer science courses (undergrad or grad) have you taken?`, 
         cs_course_name = `What are your previous computer science experiences? List course names.`, 
         cs_languages = `What programming languages do you have experience with? Check all that apply.`, 
         stat_course_name = `What are your previous statistics experiences? List course names.`, 
         other_programming_course = `What other courses have you taken that require computer programming (e.g. R, GIS, SPSS, STATA, SAS, MatLab, Mathematica, MARK, etc.)? List course names.`, 
         operating_system = `What operating system is on the computer you are bringing to the workshop?`, 
         research_experience = `Have you participated in independent or collaborative research outside the classroom?`, 
         research_amount = `If so, how much? Check all that apply.`, 
         data_collect_experience = `Do you have experience collecting your own data? Check all that apply.`, 
         data_storage = `If you have collected your own data, how did you choose to store it? Check all that apply.`, 
         reason_attend = `What is your most important reason for attending this workshop? Check all that apply.`, 
         resources_used = `What resources have you used while learning to program in R? Check all that apply.`, 
         hope_learn = `In a few words, what do you hope to learn from this workshop?`
         )


```


# Adding Workshop and Semester  

```{r}
introR <- introR %>% 
  mutate(workshop = "Introduction to R", 
         survey_time = ymd( 
           word(
             survey_time, 1)
           ), 
         semester = case_when(
           year(survey_time) == 2019 & 
             month(survey_time) %in% c(1, 2, 3, 4) ~  "spring 2019",
           year(survey_time) == 2018 & 
             month(survey_time) %in% c(8, 9, 10, 11) ~ "fall 2018"
                              )
        )


intermedR <- intermedR %>% 
  mutate(workshop = "Intermediate R", 
         survey_time = ymd( 
           word(
             survey_time, 1)
           ), 
         semester = case_when(
           year(survey_time) == 2019 & 
             month(survey_time) %in% c(1, 2, 3, 4) ~  "spring 2019",
           year(survey_time) == 2018 & 
             month(survey_time) %in% c(8, 9, 10, 11) ~ "fall 2018"
                              )
        )


wrangle <- wrangle %>% 
  mutate(workshop = "Data Wrangling in R", 
         survey_time = ymd( 
           word(
             survey_time, 1)
           ), 
         semester = case_when(
           year(survey_time) == 2019 & 
             month(survey_time) %in% c(1, 2, 3, 4) ~  "spring 2019",
           year(survey_time) == 2018 & 
             month(survey_time) %in% c(8, 9, 10, 11) ~ "fall 2018"
                              )
        )

viz <- viz %>% 
  mutate(workshop = "Data Visualization in R", 
         survey_time = ymd( 
           word(
             survey_time, 1)
           ), 
         semester = case_when(
           year(survey_time) == 2019 & 
             month(survey_time) %in% c(1, 2, 3, 4) ~  "spring 2019",
           year(survey_time) == 2018 & 
             month(survey_time) %in% c(8, 9, 10, 11) ~ "fall 2018"
                              )
        )

```


# Merging Data 

```{r}
all_survey <- full_join(introR, 
                        intermedR, 
                        by = intersect(
                          colnames(introR), 
                          colnames(intermedR)
                                      )
                        ) %>% 
              full_join(wrangle, 
                        by = intersect(
                        colnames(.), 
                        colnames(wrangle)
                                      )
                        ) %>%
              full_join(viz, 
                        by = intersect(
                        colnames(.), 
                        colnames(viz)
                                      )
                        )
```


# Cleaning Identifiers 

```{r}
identifier_function <- function(x){
  ifelse(
    str_count(x) == 6, 
    x, 
    NA
    )
}

introR <- introR %>% 
  mutate(identifier = identifier_function(identifier))

intermedR <- intermedR %>% 
  mutate(identifier = identifier_function(identifier))

wrangle <- wrangle %>% 
  mutate(identifier = identifier_function(identifier))

viz <- viz %>% 
  mutate(identifier = identifier_function(identifier))

```


# Cleaning Occupations 

```{r occupation}
all_survey <- all_survey %>% 
  mutate(occupation = case_when(grepl('I am a faculty member', occupation) ~ 
                              "Faculty", 
                            grepl('Post', occupation) ~ 
                              "Post-Doctorate",
                            grepl('I am a staff member', occupation) ~ 
                              "Staff",
                            grepl('Staff Member', occupation) ~ 
                              "Staff",
                            TRUE ~ occupation)) %>% 
  mutate(occupation = fct_explicit_na(occupation))
```


# Cleaning Departments 

```{r dept}
all_survey <- all_survey %>% 
  mutate(department = case_when(
    grepl('Faculty|Staff|Post', department) ~ 
      "NA", 
    grepl('Animal', department) ~
      "Animal & Range Sciences",
    grepl('[Aa]gricult', department) ~ 
      "Agriculture",
    grepl('[Ee]ngineering', department) ~ 
      "Engineering", 
    grepl('[Ee]ducation', department) ~ 
      "Education",
    grepl('[Bb]usiness|[Mm]arketing|biz|[Ee]conomics', department) ~ 
      "Economics or Business",
    grepl('[Ee]nvironmental [Ss]cience|[Ll][Rr][Ee][Ss]|[Ll]and', department) ~ 
      "Land Resources Environmental Science",
    grepl('[Ee]ntomo', department) ~ 
      "Land Resources Environmental Science",
    grepl('[Mm]ath|[Ss]tat|[Dd]ata', department) ~ 
      "Mathematics/Statistics/Data Science", 
    grepl('[Ee]cology|[Ff]ish|[Ww]ild', department) ~ 
      "Ecology",
    grepl('Plant|PSPP', department) ~
      "Plant Sciences & Plant Pathology", 
    grepl("CBE", department) ~ 
      "Center for Biofilm Engineering", 
    grepl('[Cc]onservation [Bb]iology', department) ~ 
      "Ecology", 
    grepl('Earth Science|Snow Science', department) ~
      "Earth Sciences", 
    grepl('Health Science', department) ~
      "Health & Human Development", 
    grepl('[Zz]oo', department) ~ 
      "Organismal Biology",
    grepl('[Pp]ol [Ss]ci', department) ~
      "Political Science", 
    grepl('[Pp]syx', department) ~
      "Psychology",
    grepl('[Mm]icrobio|[Bb]iochem|[Bb]iosci|[Gg]enetic|[Ii]mmuno', department) ~
      "Biochemistry/Microbiology",
    grepl('University|Interdisc', department) ~
      "Other",
    grepl('GIS|Rstudio|N/A', department) ~ "NA",
    TRUE ~ department
    )
)
```


# Separating Programming Languages 

```{r}
all_survey <- 
  all_survey %>% 
  mutate(python = ifelse(str_detect(cs_languages, "Python"), 
                         "Yes", 
                         "No"),
         R = ifelse(str_detect(cs_languages, "R"), 
                         "Yes", 
                         "No"),
         C = ifelse(str_detect(cs_languages, "C++"), 
                         "Yes", 
                         "No"),
         matlab = ifelse(str_detect(cs_languages, "MatLab"), 
                         "Yes", 
                         "No"),
         java = ifelse(str_detect(cs_languages, "Java"), 
                         "Yes", 
                         "No"),
         fortran = ifelse(str_detect(cs_languages, "Fortran"), 
                         "Yes", 
                         "No"),
         no_languages = case_when(str_detect(cs_languages, "None") ~ 
                                    "None",
                                  str_detect(cs_languages, 
                                             "What is a programming language?") ~
                                    "Unfamiliar"),
         other_language = ifelse(str_detect(cs_languages, "Other"), 
                         "Yes", 
                         "No"),
         SQL = ifelse(str_detect(cs_languages, "SQL"), 
                         "Yes", 
                         "No")
  )
         
```


# Separating Data Storage Methods

```{r}
all_survey <- 
  all_survey %>% 
  mutate(
    store_excel = ifelse(
      str_detect(data_storage, "Excel|.csv"),
      "Yes", 
      "No"),
    store_access = ifelse(
      str_detect(data_storage, "Access"), 
      "Yes", 
      "No"),
    store_word = ifelse(
      str_detect(data_storage, "Word"),
      "Yes", 
      "No"),
    store_paper = case_when(
      str_detect(data_storage, "paper") ~
        "Yes",
      str_detect(data_storage, "field book") ~ 
        "Yes"),
    store_text = ifelse(
      str_detect(data_storage, "Text"),
      "Yes", 
      "No"),
    store_excel = ifelse(
      str_detect(data_storage, "Excel"), 
      "Yes", 
      "No"),
    store_other = case_when(
      str_detect(data_storage, "SPSS|.sav") ~ 
        "Yes", 
      str_detect(data_storage, "image") ~ 
        "Yes", 
      str_detect(data_storage, "books") ~ 
        "Yes", 
      str_detect(data_storage, "many") ~ 
        "Yes"
      )
)
         
```


# Separating Data Collection Participation

```{r}

all_survey <- 
  all_survey %>% 
  mutate(
    self_collect = ifelse(
      str_detect(data_collect_experience, "my own data"), 
      "Yes", 
      "No"), 
    others_collect = ifelse(
      str_detect(data_collect_experience, "others"), 
      "Yes", 
      "No"),
    no_collect = ifelse(
      str_detect(data_collect_experience, "No"), 
      "Yes", 
      "NA")
)
         
```


# Separating Reasons for Attending 

```{r}
all_survey <- 
  all_survey %>% 
  mutate(
    research_help = ifelse(
      str_detect(
        tolower(reason_attend),
        "research|analyze"), 
      "Yes", 
      "No"), 
    coursework_help = ifelse(
      str_detect(
        tolower(reason_attend),
        "course|stat"), 
      "Yes", 
      "No"), 
    grad_or_career_prep = ifelse(
      str_detect(
        tolower(reason_attend),
        "grad|career|job"), 
      "Yes", 
      "No"), 
    adviser_recommend = ifelse(
      str_detect(
        tolower(reason_attend), 
        "adviser"), 
      "Yes", 
      "No"), 
    dept_recommend = ifelse(
      str_detect(
        tolower(reason_attend),
        "department"), 
      "Yes", 
      "No"), 
    flier = ifelse(
      str_detect(
        tolower(reason_attend),
        "flier"), 
      "Yes", 
      "No"), 
    network = ifelse(
      str_detect(
        tolower(reason_attend),
        "network"), 
      "Yes", 
      "No"), 
    refresh_update = ifelse(
      str_detect(
        tolower(reason_attend),
        "refresh|brush up|broaden|improve|know more"), 
      "Yes", 
      "No"), 
    professional_develop = ifelse(
      str_detect(
        tolower(reason_attend),
        "professional|students|develop"), 
      "Yes", 
      "No"
    )
    
)

```


# Separating Resources Used to Learn R 

```{r}
all_survey <- 
  all_survey %>% 
  mutate(
    no_resources = case_when(
      resources_used == "?" ~ 
        "Yes", 
      str_detect(
        tolower(resources_used),
        "n/a|haven't learned|haven't used yet|none") ~ 
        "Yes"
      ), 
    previous_workshops = ifelse(
      str_detect(
        tolower(resources_used),
        "your|these courses|this course|this workshop"), 
      "Yes", 
      "No"), 
    adviser_resource = ifelse(
      str_detect(
        tolower(resources_used),
        "adviser"), 
      "Yes", 
      "No"), 
    course_resources = ifelse(
      str_detect(
        tolower(resources_used),
        "course material"), 
      "Yes", 
      "No"), 
    book_resources = ifelse(
      str_detect(
        tolower(resources_used),
        "books"), 
      "Yes", 
      "No"), 
    lab_resources = ifelse(
      str_detect(
        tolower(resources_used),
        "lab mates"), 
      "Yes", 
      "No"), 
    peer_resources = ifelse(
      str_detect(
        tolower(resources_used),
        "peers"), 
      "Yes", 
      "No"), 
    professor_resources = ifelse(
      str_detect(
        tolower(resources_used),
        "professor"), 
      "Yes", 
      "No"), 
    internet_resources = ifelse(
      str_detect(
        tolower(resources_used),
        "internet|youtube"), 
      "Yes", 
      "No")

  )

```


# Extracting Clean Data 

```{r}
write.csv(all_survey, "all_ws_presurvey.csv")
```

